AbxD01 Analysis

### 2015-01-26 abxD01_analysis.Rmd
figure update

avg14<-tapply(metroD0$Otu014, metroD0$order, mean)
sd14<-tapply(metroD0$Otu014, metroD0$order, sd)

avg7<-tapply(metroD0$Otu007, metroD0$order, mean)
sd7<-tapply(metroD0$Otu007, metroD0$order, sd)

avg09<-tapply(metroD0$Otu009, metroD0$order, mean)
sd09<-tapply(metroD0$Otu009, metroD0$order, sd)

@@

avg12<-tapply(metroD0$Otu012, metroD0$order, mean)
sd12<-tapply(metroD0$Otu012, metroD0$order, sd)

@@

#Now graphing:
par(mfrow=c(4, 3))

par(mar=c(2, 4, 2, 3) +0.1)
plot01<-barplot(avg01, col="darkblue", cex.axis=1.3, xaxt="n") 
error.bar(plot01, avg01, sd01) #plot SD

par(mar=c(2, 3, 2, 3) +0.1)
plot03<-barplot(avg03, col="steelblue", cex.axis=1.3, xaxt="n")
error.bar(plot03, avg03, sd03) #plot SD

plot11<-barplot(avg11, col="darkgreen", cex.axis=1.3, xaxt="n")
error.bar(plot11, avg11, sd11) #plot SD

par(mar=c(2, 4, 2, 3) +0.1)
plot02<-barplot(avg02, col="darkred", cex.axis=1.3, xaxt="n")
error.bar(plot02, avg02, sd02) #plot SD

par(mar=c(2, 3, 2, 3) +0.1)
plot05<-barplot(avg05, col="orange2", cex.axis=1.3, xaxt="n")
error.bar(plot05, avg05, sd05) #plot SD

plot04<-barplot(avg04, col="gold1", cex.axis=1.3, xaxt="n")
error.bar(plot04, avg04, sd04) #plot SD

par(mar=c(2, 4, 2, 3) +0.1)
plot16<-barplot(avg16, col="deeppink3", cex.axis=1.3, xaxt="n")
error.bar(plot16, avg16, sd16) #plot SD
axis(1, at=plot16, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

par(mar=c(2, 3, 2, 3) +0.1)
plot7<-barplot(avg7, col="blueviolet", cex.axis=1.3, xaxt="n")
error.bar(plot7, avg7, sd7) #plot SD
axis(1, at=plot7, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

plot06<-barplot(avg06, col="black", cex.axis=1.3, xaxt="n")
error.bar(plot06, avg06, sd06) #plot SD
axis(1, at=plot06, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

>>>>

# avg14<-tapply(metroD0$Otu014, metroD0$order, mean)
# sd14<-tapply(metroD0$Otu014, metroD0$order, sd)

avg07<-tapply(metroD0$Otu007, metroD0$order, mean)
sd07<-tapply(metroD0$Otu007, metroD0$order, sd)

# avg09<-tapply(metroD0$Otu009, metroD0$order, mean)
# sd09<-tapply(metroD0$Otu009, metroD0$order, sd)

@@

# avg12<-tapply(metroD0$Otu012, metroD0$order, mean)
# sd12<-tapply(metroD0$Otu012, metroD0$order, sd)

@@

#Now graphing:
par(mfrow=c(3, 3))

par(mar=c(2, 4, 2, 3) +0.1)
plot01<-barplot(avg01, col="black", cex.axis=1.3, xaxt="n") 
#error.bar(plot01, avg01, sd01) #plot SD
axis(1, at=plot01, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

# par(mar=c(2, 4, 2, 3) +0.1)
# plot14<-barplot(avg14, col="black", cex.axis=1.3, xaxt="n") 
# #error.bar(plot14, avg14, sd14) #plot SD
# axis(1, at=plot14, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

par(mar=c(2, 3, 2, 3) +0.1)
plot07<-barplot(avg07, col="black", cex.axis=1.3, xaxt="n")
#error.bar(plot07, avg07, sd07) #plot SD
axis(1, at=plot07, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

# par(mar=c(2, 3, 2, 3) +0.1)
# plot09<-barplot(avg09, col="black", cex.axis=1.3, xaxt="n")
# #error.bar(plot09, avg09, sd09) #plot SD
# axis(1, at=plot09, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

par(mar=c(2, 4, 2, 3) +0.1)
plot02<-barplot(avg02, col="black", cex.axis=1.3, xaxt="n")
#error.bar(plot02, avg02, sd02) #plot SD
axis(1, at=plot02, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

par(mar=c(2, 4, 2, 3) +0.1)
plot13<-barplot(avg13, col="black", cex.axis=1.3, xaxt="n")
#error.bar(plot13, avg13, sd13) #plot SD
axis(1, at=plot13, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

par(mar=c(2, 3, 2, 3) +0.1)
plot03<-barplot(avg03, col="black", cex.axis=1.3, xaxt="n")
#error.bar(plot03, avg03, sd03) #plot SD
axis(1, at=plot03, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

par(mar=c(2, 3, 2, 3) +0.1)
plot05<-barplot(avg05, col="black", cex.axis=1.3, xaxt="n")
#error.bar(plot05, avg05, sd05) #plot SD
axis(1, at=plot05, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

par(mar=c(2, 3, 2, 3) +0.1)
plot08<-barplot(avg08, col="black", cex.axis=1.3, xaxt="n")
#error.bar(plot08, avg08, sd08) #plot SD
axis(1, at=plot08, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

par(mar=c(2, 3, 2, 3) +0.1)
plot06<-barplot(avg06, col="black", cex.axis=1.3, xaxt="n")
#error.bar(plot06, avg06, sd06) #plot SD
axis(1, at=plot06, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

par(mar=c(2, 3, 2, 3) +0.1)
plot04<-barplot(avg04, col="black", cex.axis=1.3, xaxt="n")
#error.bar(plot04, avg04, sd04) #plot SD
axis(1, at=plot04, labels=c("D0", "D0 Recovered"), cex.axis=1.7)

# par(mar=c(2, 3, 2, 3) +0.1)
# plot12<-barplot(avg12, col="black", cex.axis=1.3, xaxt="n")
# #error.bar(plot12, avg12, sd12) #plot SD
# axis(1, at=plot12, labels=c("D0", "D0 Recovered"), cex.axis=1.7)
#

# par(mar=c(2, 4, 2, 3) +0.1)
# plot11<-barplot(avg11, col="black", cex.axis=1.3, xaxt="n")
# error.bar(plot11, avg11, sd11) #plot SD
# axis(1, at=plot11, labels=c("D0", "D0 Recovered"), cex.axis=1.7)
# 
# par(mar=c(2, 4, 2, 3) +0.1)
# plot16<-barplot(avg16, col="balck", cex.axis=1.3, xaxt="n")
# error.bar(plot16, avg16, sd16) #plot SD
# axis(1, at=plot16, labels=c("D0", "D0 Recovered"), cex.axis=1.7)
